Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-05-15 cthpc-2017/paper.tex
Re-arranged the system and xenomai architecture image
Change budget form NTD to USD and correct the spelling

\begin{figure}
	\centering
	\includegraphics[width=3in]{img/arch.png}
	\caption{System Architecture}
	\label{fig:overall_arch}
\end{figure}

@@

Despite limited the budget shown in table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car Interaction and route planning.

\begin{table}
	\centering
	\caption{Bill Of Materials}
	\label{hardware_list}
	\begin{tabular}{ll}
		Hardware                & Budgets  \\
		Raspberry Pi3 Model B   & 1200 NTD \\
		Raspberry Pi camera     & 698 NTD  \\
		2S LiPo battery 1300mAh & 240 NTD  \\
		Sandisk 16G microSD     & 185 NTD  \\
		L298N motor driver      & 263 NTD  \\
		Car frame               & 375 NTD  \\
		DC voltage regulator    & 105 NTD  \\
		Total                   & 3066 NTD
	\end{tabular}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=3in]{img/xeno_arch.png}
	\caption{Cobalt core in Xenomai 3}
	\label{fig:xeno_arch}
\end{figure}

Most system use pulse width modulation (PWM) to simulate the analog signal for smooth motor controlling. PWM signals are often generated by certain hardware. On the contrary, using general-purpose input/output (GPIO) to simulate PWM signals is known as software PWM. We implement the later as a Xenomai kernel-mode real-time task to ensure the precision of PWM signal generation, named after KsoftPWM, for closed-loop control system, benefiting from the limination of system call overhead and potential locks.

@@

Figure \ref{fig:extrinsic} show the result of Homography transformation, we exploit the transformation for the lane detectoion algorithm, the result is usually called the bird view image or inverse perspective mapping.

@@

\bibliographystyle{IEEEtran}
\bibliography{references}

>>>>

\FloatBarrier

\begin{figure}
	\centering
	\includegraphics[width=2.3in]{img/soft_arch.jpg}
	\caption{System Architecture}
	\label{fig:overall_arch}
\end{figure}

@@

Despite limited the budget shown in table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car interaction and route planning.

\begin{table}
	\centering
	\caption{Bill Of Materials}
	\label{hardware_list}
	\begin{tabular}{ll}
		Hardware                & Budgets  \\
		Raspberry Pi3 Model B   & 39.79 USD \\
		Raspberry Pi camera     & 23.15 USD  \\
		2S LiPo battery 1300mAh & 7.96 USD  \\
		Sandisk 16G microSD     & 6.13 USD  \\
		L298N motor driver      & 8.72 USD  \\
		Car frame               & 12.44 USD  \\
		DC voltage regulator    &  3.48 USD  \\
		Total                   & 101.67 USD
	\end{tabular}
\end{table}

@@

\FloatBarrier
\begin{figure}
	\centering
	\includegraphics[width=3in]{img/xeno_arch.jpg}
	\caption{Cobalt core in Xenomai 3}
	\label{fig:xeno_arch}
\end{figure}

Most system use pulse width modulation (PWM) to simulate the analog signal for smooth motor controlling. PWM signals are often generated by certain hardware. On the contrary, using general-purpose input/output (GPIO) to simulate PWM signals is known as software PWM. We implement the later as a Xenomai kernel-mode real-time task to ensure the precision of PWM signal generation, named after KsoftPWM, for closed-loop control system, benefiting from the elimination of system call overhead and potential locks.

@@

Figure \ref{fig:extrinsic} show the result of Homography transformation, we exploit the transformation for the lane detection algorithm, the result is usually called the bird view image or inverse perspective mapping.

@@

\bibliographystyle{IEEEtran}
\bibliography{references.bib}
